
The \h\ ion has long been recognized as an important source of
continuum opacity in the sun at visible
wavelengths. \citet{Wildt1939a,Wildt1939b} was among the first to
recognize this.  The \h\ ion is, quite simply, a hydrogen atom with an extra electron.  This extra electron
has a relatively low ionization potential of $\chi = 0.754$ eV
(\citealt{carroll2007introduction}, which corresponds to a photon
wavelength of $\sim 16500$\AA.  It is, in part, due to this low
ionization potential that \h\ provides such  a significant contribution to the opacity of the sun's
photosphere in the visible and near-infrared.  \h\ opacities are relevant in all
stars cooler than F0 (\citealt{carroll2007introduction}). \h\
abundance (and therefore its contribution to the opacity) is sensitive 
to temperature and to the abundance of low-\chii\ metals
(\citealt{hansen1994stellar}), primarily the alkali and alkaline earth metals.  The temperature dependence of \h\
abundance can be characterized qualitatively as follows: the gas needs
to be of high enough temperature to allow free electrons (ionized from
low-\chii\ metals as well as some hydrogen) to exist.  The gas,
however, also needs to be of low enough temperature that the
lightly-bound second electrons are not quickly stripped from the
hydrogen atoms either through collisional ionization or a large flux
of photons.  Thus, if the temperature is too low \h\ ions will not be
produced and if the temperature is too high \h\ ions won't survive
long enough to make significant contributions to the opacity.

As far as a qualitative picture for opacity dependence on metallicity,
well, that's where figure 4.4 comes in.

Note to Joshua:  \cite{hansen1994stellar} figure 4.4 provides a figure
of \h\ opacities, I think the temperature dependence.
